Python as a machine learning language: experiences from the scikit-learn project

### 2013-04-27 api.tex
citations for kernel approximations
Thanks @amueller!

A \texttt{fit} method is present even on objects
that perform seemingly mundane tasks such as vectorizing text documents
for subsequent learning.
Such classes, however, can be said to learn their vocabulary
from the training corpus,
and follow the conventions set out above.
Even those estimators that are entirely stateless and therefore
do not require a \texttt{fit} method to perform useful work,
nevertheless have such a method for consistency and composibility,
and to perform parameter validation.
Examples of this latter kind of objects are the normalizing transformer,
kernel approximation transformers,
and two feature extraction classes that implement the ``hashing trick''
\citep{weinberger2009}.

>>>>

A \texttt{fit} method is present even on objects
that perform seemingly mundane tasks such as vectorizing text documents
for subsequent learning.
Such classes, however, can be said to learn their vocabulary
from the training corpus,
and follow the conventions set out above.
Even those estimators that are entirely stateless and therefore
do not require a \texttt{fit} method to perform useful work,
nevertheless have such a method for consistency and composibility,
and to perform parameter validation.
Examples of this latter kind of objects are the normalizing transformer,
kernel approximation transformers
\citep{rahimi2007random, li2010random, vedaldi2010efficient},
and two feature extraction classes that implement the ``hashing trick''
\citep{weinberger2009}.
